---
title: "marinerData package"
output:
  rmarkdown::html_document
vignette: |
  %\VignetteIndexEntry{marinerData package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The *marinerData* package provides some small 
Hi-C files for the *mariner* package vignettes and tests.

```{r}
library(marinerData)
hicFiles <- c(
    LEUK_HEK_PJA27_inter_30.hic(),
    LEUK_HEK_PJA30_inter_30.hic()
)
names(hicFiles) <- c("FS", "WT")
hicFiles
```

It also provides two sets of loop calls. The following
two files correspond to the test Hi-C files described
above.

```{r}
library(marinerData)
nha9Loops <- c(
  FS_5kbLoops.txt(),
  WT_5kbLoops.txt()
)
```

Additionally, loop calls from a THP-1 activation
timecourse are also provided. These cells were
exposed to LPS & IF-G for 0, 30, 60, 90, 120, 240,
360, or 1440 minutes. The dataset is abbreviated
as LIMA (LPS/IF-G Induced Macrophage Activation).

```{r}
library(marinerData)
limaLoops <- c(
  LIMA_0000.bedpe(),
  LIMA_0030.bedpe(),
  LIMA_0060.bedpe(),
  LIMA_0090.bedpe(),
  LIMA_0120.bedpe(),
  LIMA_0240.bedpe(),
  LIMA_0360.bedpe(),
  LIMA_1440.bedpe()
)
names(limaLoops) <- c(
  "LIMA_0000",
  "LIMA_0030",
  "LIMA_0060",
  "LIMA_0090",
  "LIMA_0120",
  "LIMA_0240",
  "LIMA_0360",
  "LIMA_1440"
)
limaLoops
```

# Session information

```{r}
sessionInfo()
```
